On particular diameter bounds for integral point sets in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-07 AvdMomZvol_rails/Article.tex
[AMZr] Remove a TODO note
[AMZr] Move the notation to where itisused first

@@

%TODO: rephrase?

@@

\begin{figure}[h!]
\center{\includegraphics[width=0.7\linewidth]{17_2210_1_acc4a56887abb3c3a315712ea083f0e7_centered_circle.png}}
\parbox{0.7\linewidth}{\caption{A centered-circular PIPS of cardinality 17 and diameter 2210}
\label{17_2210_1_acc4a56887abb3c3a315712ea083f0e7_centered_circle.png}}
\end{figure}

@@

Below we give the examples of planar integral point sets and the corresponding
estimates of the function $d(m, n)$ for $n = 2m + k$, $3 \leq k \leq 36$.
For the sake of brevity, we use the notation
$\sqrt{p}/q * \{ (x_1,y_1), ...,$ $ (x_n, y_n)  \}$
from~\cite{our-ped-2018,our-pmm-2018,our-vmmsh-2018},
which means that each abscissa is multiplied by $1/q$
and each ordinate is multiplied by $\sqrt{p}/q$,  that is
$$
	\sqrt{p}/q * \{ (x_1,y_1), ..., (x_n, y_n)  \}
	=
	\left\{ \left(\frac{x_1}{q},\frac{y_1\sqrt{p}}{q}\right), ..., \left(\frac{x_n}{q},   \frac{y_n\sqrt{p}}{q}\right)  \right\}.
$$

>>>>

For the sake of brevity, we will hereafter use the notation
$\sqrt{p}/q * \{ (x_1,y_1), ...,$ $ (x_n, y_n)  \}$
from~\cite{our-ped-2018,our-pmm-2018,our-vmmsh-2018},
which means that each abscissa is multiplied by $1/q$
and each ordinate is multiplied by $\sqrt{p}/q$,  that is
$$
	\sqrt{p}/q * \{ (x_1,y_1), ..., (x_n, y_n)  \}
	=
	\left\{ \left(\frac{x_1}{q},\frac{y_1\sqrt{p}}{q}\right), ..., \left(\frac{x_n}{q},   \frac{y_n\sqrt{p}}{q}\right)  \right\}.
$$

@@

@@

\begin{figure}[htbp]
	\includegraphics[width=.42\linewidth]{17_2210_1_acc4a56887abb3c3a315712ea083f0e7_centered_circle.png}
	\hfill
	\includegraphics[width=.545\linewidth]{15_3364_91_30e991f82a54fb9caeca5b6a6776b981_X.png}
	\\
	\parbox{.37\linewidth}{\caption{A centered-circular PIPS of cardinality 17 and diameter 2210}
	\label{17_2210_1_acc4a56887abb3c3a315712ea083f0e7_centered_circle.png}}
	\hfill
	\parbox{.5\linewidth}{\caption{A scissors PIPS of cardinality 15 and diameter 3364}
	\label{15_3364_91_30e991f82a54fb9caeca5b6a6776b981_X.png}}
\end{figure}

@@

Below we give the examples of planar integral point sets and the corresponding
estimates of the function $d(m, n)$ for $n = 2m + k$, $3 \leq k \leq 36$.
